Bayes Computational Method

### 2020-02-11 Paper.Rmd
paper update no outline

---
title: "Paper"
output: pdf_document
---

@@

## Outline
- Introduction to problem and history
  - Bayesian paradigm
  - How computing fits into bayesian paradigm
  - Common terms that will be used in rest of paper
  - Provide basic code example
- General Bayesian computational settings
  - Chains
    - Greta
  - Iterations
  - Warmup
    - STAN/Bugs uses warmup as a part of iterations, Jags/greta/Nimble have it seperate.
  - Thinning
  - initial value specification
- Each sampler
  - BUGS - 
    - WINE
    - Debugging
  - Jags
  - Nimble
    - Crashes
  - STAN
    - RDS file
  - greta
- Common coding techniques for each language
  - Model specification
    - Truncated normal
    - matrix multiplication
    - Flat priors
    - parameter order
      - Binomial Stan has (n,p), rest have (p,n)
    - Equations inside distribution parameters
  - Data specification
    - Nimble constants
    - Nimble initial values
    - initial values for each 
- Benchmarking
  - Run time
  - Memory allocation
  - Computational accuracy
  - Benchmarking files
- Folder design
  - General model type
    - Simple conjugate models
    - Regression models
    - Time Series models
    - Survival models
    - 8 Schools
  - Specific model type
  - Scripts for each method 
  - Benchmarking
- Here package
- Models Used

\newpage

@@

## BUGS

>>>>

---
title: "Bayes Computational Method"
output: pdf_document
---

@@

@@

## OpenBUGS
